\cvsection{Publications}
\begin{cventries}
    \pubentry
        {Temporal Action Localization via Structured Maximal Sums}
        {Zehuan Yuan, \textbf{Jonathan Stroud}, Tong Lu, Jia Deng}
        {IEEE Conference on Computer Vision and Pattern Recognition (CVPR)}
        {July, 2017.}
        {Honolulu, Hawaii.}
        {}
    \pubentry
        {The Michigan Data Science Team: A Student Organization for Machine Learning Challenges}
        {\textbf{Jonathan Stroud}, Alex Chojnacki, Jacob Abernethy}
        {Neural Information Processing Systems (NIPS) Workshop on Challenges in Machine Learning}
        {December, 2016.}
        {Barcelona, Spain.}
        {}
    \pubentry
        {Flint Water Crisis: Data-Driven Risk Assessment Via Residential Water Testing}
        {Jacob Abernethy, Cyrus Anderson, Chengyu Dai, Arya Farahi, Linh Nguyen, Adam Rauh, Eric Schwartz, Wenbo Shen, Guangsha Shi, \textbf{Jonathan Stroud}, Xinyu Tan, Jared Webb, Sheng Yang}
        {Bloomberg Data For Good Exchange}
        {September, 2016.}
        {New York City, New York.}
        {}
    \pubentry
        {Data Science in Service of Performing Arts: Applying Machine Learning to Predicting Audience Preferences}
        {Jacob Abernethy, Cyrus Anderson, Alex Chojnacki, Chengyu Dai,
          John Dryden, Eric Schwartz, Wenbo Shen, \textbf{Jonathan
            Stroud}, Laura Wendlandt, Sheng Yang, Daniel Zhang}
        {Bloomberg Data For Good Exchange}
        {September, 2016.}
        {New York City, New York, USA.}
        {}
\end{cventries}
